Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
removing extra space

Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors and as noted in the introduction (\S\ref{sec:intro}), there is evidence that authors follow instructions if they exist ~\cite{10.1371/journal.pone.0136631}.

>>>>

Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors and as noted in the introduction (\S\ref{sec:intro}), there is evidence that authors follow instructions if they exist~\cite{10.1371/journal.pone.0136631}.
